Self Regulation Ontology Retest Analyses

### 2018-04-27 code/SRO_Retest_Analyses.Rmd
refactoring

# write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/lit_emp_cor_out.csv')

@@

```{r echo=FALSE}
rm(tmp, rel_comp, boot_comp, mod1, mod2, mod3, mod4, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
```

@@

@@

p5_t <- tmp %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc, group=dv)) + 
  geom_violin(fill='#F8766D', position = 'identity')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=43))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value),
            n = n()) %>%
  mutate(cvl = qt(0.025, n-1),
         cvu = qt(0.975, n-1),
         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
         ciu = mean_pct+(sd_pct*cvu)/sqrt(n)) %>%
  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance")), mean_pct, color=task))+
  geom_point(position=position_dodge(width = 0.25), size=5)+
  geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
  theme_bw()+
  xlab('')+
  ylab('Percent')+
  theme(legend.title = element_blank(),
        legend.text = element_text(size=14),
        axis.text = element_text(size=12),
        axis.title.y = element_text(size=12))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))

>>>>

write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')

@@

```{r echo=FALSE}
rm(tmp, rel_comp, mod1, mod2, mod3, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
```

@@

```{r}
table(rel_df$task)
```

@@

p5_t <- tmp %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=43))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value),
            n = n()) %>%
  mutate(cvl = qt(0.025, n-1),
         cvu = qt(0.975, n-1),
         cil = mean_pct+(sd_pct*cvl)/sqrt(n),
         ciu = mean_pct+(sd_pct*cvu)/sqrt(n)) %>%
  ggplot(aes(factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance")), mean_pct, color=task))+
  # geom_point(position=position_dodge(width = 0.25), size=5)+
  # geom_errorbar(aes(ymin=mean_pct-sd_pct, ymax=mean_pct+sd_pct), position=position_dodge(width = 0.25), width=0, size=2)+
  geom_errorbar(aes(ymin=cil, ymax=ciu), position=position_dodge(width = 0.25), width=0, size=2)+
  theme_bw()+
  xlab('')+
  ylab('Percent')+
  theme(legend.title = element_blank(),
        legend.text = element_text(size=14),
        legend.position = 'bottom',
        axis.text = element_text(size=12),
        axis.title.y = element_text(size=12))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))
